Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-07 WSSSPE3/report/WSSSPE3_review.tex
add Alica Allen's talk

\item \textbf{Alice Allen: \textit{We're giving away the store! (Merchandise not
included)}}

>>>>

\item \textbf{Alice Allen: \textit{We're giving away the store! (Merchandise not
included)}}
Alice Allen described the Astrophysics Source Code Library (ascl.net), an increasingly
used way to obtain a unique ID for astrophysics software that is indexed by indexing
services and can be cited. ASCL offers clones of existing infrastructure, provides server
space and computing resources, shares innovations, and permits moves elsewhere. In turn,
users have to provide a domain nam, control and configure their site and use it as
intended, gather their codes to their liking, share innovations and protect the
provided computing environment.
